Expanding the Power of Lens Synthesis \\ (talk proposal)

### 2019-02-19 papers/BXProposal/main.tex

\begin{abstract}
  {\color{dkblue} \emph{AFM: I will remove this from the submission, but am including it in the
    document for people to review. It is due today (February 12)}} Recent work
  has shown how to synthesize a class of string bijections from regular
  expression specifications. These bijective string transformations can be
  useful for synchronizing simple data formats, but many interesting formats
  require non-bijective lenses. In this talk, we show how to expand the class of
  synthesized transformations beyond bijections to quotient lenses and a large
  subset of full symmetric lenses (including all the standard asymmetric lenses)
  through lightweight user annotations that help identify a ``bijective core.''
\end{abstract}

@@

Instead of manually writing explicit canonization and projection functions, we
consider an alternative approach: by annotating our regular expressions with
canonization and projection annotations, we can write our data formats and find
the bijective core in a single step. This approach has already been employed in
synthesizing bidirectional transformations that are bijections (up to
quotients)~\cite{maina+:quotient-synthesis}, but here we extend it with projections as well.

@@

Now, with annotated regular expressions, we can synthesize the composers lens much
more compactly.
%
\begin{lstlisting}
  let composers'  = synth full_composers' <=> composers_nodates'
\end{lstlisting}
%
Synthesizing with these annotated regular expressions performs the same steps
that we previously did manually: it breaks the lens into concatenation and
normalization subcomponents, sends the bijective core to the existing synthesis
algorithm, and composes the generated subcomponents with the synthesized
bijective core.

>>>>

\vspace*{-3em}

\begin{abstract}
  Recent work
  has shown how to synthesize a class of string bijections from regular
  expression specifications. These bijective string transformations can be
  useful for synchronizing simple data formats, but many interesting formats
  require non-bijective lenses. In this talk, we show how to expand the class of
  synthesized transformations beyond bijections to quotient lenses and a large
  subset of full symmetric lenses (including all the standard asymmetric lenses)
  through lightweight user annotations that help identify a ``bijective core.''
\end{abstract}

@@

Instead of writing explicit canonization and projection functions, we
consider an alternative approach: by annotating our regular expressions with
canonization and projection annotations, we can write our data formats and find
the bijective core in a single step. This approach has already been employed in
synthesizing bidirectional transformations that are bijections (up to
quotients)~\cite{maina+:quotient-synthesis}, here we extend it with projections as well.

@@

Now, with annotated regular expressions, we can synthesize the composers lens much
more compactly.
%
\begin{lstlisting}
  let composers'  = synth full_composers' <=> composers_nodates'
\end{lstlisting}
%
